---
title: "Activity 2.6 - Exploratory Data Analysis: Merging Data Sets and Visualizing Spatial Data"
author: "PURPLE"
date: "09-24-2019"
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
install.packages("tidyverse")
library(tidyverse)
```

### Load data

```{r load-data, message=FALSE}
dennys <- read_csv("data/dennys.csv")
laquinta <- read_csv("data/laquinta.csv")
states <- read_csv("data/states.csv")
```


### Exercise 1

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 2

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 3

...


### Exercise 4

...


### Exercise 5

...


### Exercise 6

...



### Exercise 7

...


### Exercise 8

...


### Exercise 9

...


### Exercise 10

...


### Exercise 11

...


### Exercise 12

...
