---
title: "Activity 2.6 - Exploratory Data Analysis: Merging Data Sets and Visualizing Spatial Data"
author: "PURPLE"
date: "09-24-2019"
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
#install.packages("tidyverse")
library(tidyverse)
```

### Load data

```{r load-data, message=FALSE}
dennys <- read_csv("data/dennys.csv")
laquinta <- read_csv("data/laquinta.csv")
states <- read_csv("data/states.csv")
```


### Exercise 1

```{r Dennys-variables-observations}
dim(dennys)
head(dennys)
names(dennys)
```
Dimension's of Denny's are 1643 rows and 6 columns. Each row is the observation of the physical location of each Denny's in the USA. Each variable is an aspct of either its mailing address or geospatial location.
### Exercise 2

```{r Quinta-variables-observations}
dim(laquinta)
head(laquinta)
names(laquinta)
```
Dimension's of laquinta's are 909 rows and 6 columns. Each row is the observation of the physical location of each La Quinta's in the USA. Each variable is an aspct of either its mailing address or geospatial location

### Exercise 3

La Quinta has locations outside of the United States in South America (e.g. Argentina, Brazil, and Chile), Africa (e.g. Ethiopia, Morocco, Nigeria, etc.), Asia (e.g China), Europe, Central America, Australia, but none in the Middle East according to their search tool.
According to their website and the dataset, Denny's does not have locations outside the USA; but according to their wiki, Denny's has locations outside the USA in Asia (e.g. Japan), Africa (e.g. United Arab Emirates), Europe (e.g. UK), Canada, the Caribbean (Curacao), and Mexico among others. 

### Exercise 4

Use an anti-join (filtering mutate function) to retain only the rows in the la quinta dataset that are not in the dennys dataset by state name.

### Exercise 5

```{r}
dennys%>%
  filter(!(state %in% states$abbreviation))
```


### Exercise 6

```{r}
dennys <- dennys %>%
  mutate(., country = "United States")
```



### Exercise 7

```{r la-quinta-locations-outside-the-us}
laquinta%>%
  filter(!(state %in% states$abbreviation))
```
La Quintas in the dataset outside the US include ones in Mexico, Columbia, Canada, and Honduras.

### Exercise 8

```{r}
laquinta<-laquinta %>% 
  mutate(country = case_when(
    state %in% state.abb ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT" ~ "Columbia",
    state %in% c("QR", "CH","PU","NL","VE","AG","SL") ~ "Mexico",
    state == "FM" ~ "Honduras"
  ))
laquinta
```


### Exercise 9
```{r}
dennys %>%
  count(state) %>%
  arrange(n)
```

```{r}
laquinta %>%
  count(state) %>%
  arrange(n)
```
States with the least Denny's locations are Alaska, Delaware, DC, Iowa, Louisiana, Montana, North Dakota, New Hampshire, South Dakota, Vermont, West Virginia, and Wyoming. 

States with the least La Quinta locations are Alaska, Iowa, Maine, Michigan, New Hampshire, Rhode Island, South Dakota, Vermont, West Virginia, and Wyoming.

This makes sense (for the most part) because most of the states are very small and/or sparsely populated.

### Exercise 10
```{r}
dennys %>%
  count(state) %>%
  inner_join(states, by = c("state" = "abbreviation")) %>%
  mutate(per1000SqMi = (n/area)*1000) %>%
  arrange(desc(per1000SqMi))
```

The states with the most Denny's locations per thousand square miles are DC, Rhode Island, California, and Connecticut.

```{r}
laquinta %>%
  count(state) %>%
  inner_join(states, by = c("state" = "abbreviation")) %>%
  mutate(per1000SqMi = (n/area)*1000) %>%
  arrange(desc(per1000SqMi))
```

The states with the most La Quinta locations per thousand square miles are Rhode Island, Florida, Connecticut, and Maryland.

### Exercise 11
```{r}
dennys <- dennys %>% 
  mutate(establishment = "Denny's")
laquinta <- laquinta %>% 
  mutate(establishment = "La Quinta")
```

```{r}
dennys_laquinta <- bind_rows(dennys, laquinta)
```

```{r}
ggplot(dennys_laquinta, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point()
```

``` {r 11}
michigan <- dennys_laquinta %>%
  filter(state=="MI")
ggplot(michigan, mapping = aes(x = longitude, y = latitude, color = establishment, alpha=.01)) +
  geom_point()
```
His joke somewhat holds up, in the sense that the few La Quinta locations in Michigan are all somewhat close to a Denny's.

### Exercise 12

``` {r twelve}
texas <- dennys_laquinta %>%
  filter(state=="TX")
ggplot(texas, mapping = aes(x = longitude, y = latitude, color = establishment, alpha=.01)) +
  geom_point()
```
His joke holds up less here than Michigan because there are far more La Quintas in Texas than Denny's. They are next to each other in the major cities, but where there are sparsely located La Quintas, there isn't always a Denny's nearby. The joke is still funny though.